% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org

% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca

% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com

% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932

% (c) 2012 Andrew Solomon <andrewsolomon.edu@gmail.com> http://andysolomon.github.com
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

\newlength{\outerbordwidth}

\pagestyle{empty}

\raggedbottom

\raggedright

\usepackage[svgnames]{xcolor}

\usepackage{framed}

\usepackage{tocloft}

%-----------------------------------------------------------

%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars

\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)

\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------

%Margin setup

\setlength{\evensidemargin}{-0.25in}

\setlength{\headheight}{-0.25in}

\setlength{\headsep}{0in}

\setlength{\oddsidemargin}{-0.25in}

\setlength{\paperheight}{11in}

\setlength{\paperwidth}{8.5in}

\setlength{\tabcolsep}{0in}

\setlength{\textheight}{9.75in}

\setlength{\textwidth}{7in}

\setlength{\topmargin}{-0.3in}

\setlength{\topskip}{0in}

\setlength{\voffset}{0.1in}

%-----------------------------------------------------------

%Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}

  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}

    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}

    \end{shaded}

  }\vspace{-5pt}

}

\newcommand{\ressubheading}[4]{

\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}

		\textbf{#1} & #2 \\

		\textit{#3} & \textit{#4} \\

\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Andrew Solomon} & \textbf{\today} \\

Life-time Student & andrewsolomon.edu@gmail.com \\

Atlanta, GA & andysolomon.github.com / 678-613-5631\\

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{Albany State University}{Albany, GA}{B.Sc. Computer Science}{2005 - 2010}

	\begin{itemize}

		\resitem{Department of Math and Computer Science (Research Assistant, 4 years)}

		\resitem{Emphasis on machine learning/data mining and algorithm design/software development related to bioinformatics and IT security}

		\resitem{Graduated with minors in Business and Mathematics}

	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Javascript (intermediate):} Development (jQuery, Backbone, Express, Geddy, jQuery Mobile), Testing/Configuration (Jasmine, Require)

\item {\bf Ruby (beginner):} Development (Rails, Sinatra, Jekyll), Testing/Configuration (Rspec, Cucumber, Bundler)

\item {\bf PHP (beginner):} Development (Codeigniter, Wordpress)

\item {\bf HTML/CSS (advanced):} Development (Haml, Jade, Sass, Less, Canvas, WebSockets), Testing/Configuration (Compass)

\item {\bf Unix:} Systems (Ubuntu, CentOS, Mac), Tools (Git, Vim, Tmux, ZSH)

\item Discovering and implementing new ideas. Give me an API and a problem and I will figure it out.

\item Diverse background in Math, Computer Science, and Biology allows me to communicate to a wide scientific and general audience and begin contributing to any group immediately.

\item I have worked in many places in a myriad of fields. I can readily learn and adapt to a new discipline, area or environment and start pushing real results quickly.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research and Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{The Monticello Corporation}{Atlanta, GA}{Senior Software Development}{2010-Current Position}

	\begin{itemize}

		\resitem{Developed and maintained commercial SAAS software in \texttt{PHP} and \texttt{Javascript}}

    \resitem{Implemented and designed 3rd party API functionality to allow users to freely interact with Google Docs API}

	\end{itemize}

\item

	\ressubheading{Blackbox Network Services}{Fitzgerald, GA}{Computer Data Technician}{2010}

	\begin{itemize}

		\resitem{Setup, configured, and maintained Wal-Mart's complex LAN and WLAN implementation.  Gained experience setting up and maintaing Cisco routers and swithces, along with VLAN and Voice-Over-IP solutions}

    \resitem{Made key schematically design routines for proper planning and installinton of wired and wireless systems}

	\end{itemize}

\item 

	\ressubheading{Albany State University}{Albany, GA}{Researcher in Information Assurance program under Dr. Robert Owor}{Summer 2009}

	\begin{itemize}

		\resitem{Wrote \textbf{open source} web application in \texttt{PHP} and \texttt{Javascript} allowing students to explore research options in Information Assurance}

    \resitem{Contributed in setting up information security workshops with Alabama A and M, Auburn University, Albany Tech, and Darton College}

	\end{itemize}

\item

	\ressubheading{Albany State University}{Albany, GA}{Research Assistant in Perl for Bioinformatics under Dr. Khalil Dajani}{2006-2008}

	\begin{itemize}

		\resitem{Developed minor \textbf{open source} desktop utility in \texttt{Perl}, used to analyze DNA sequencing of any being}
  
		\resitem{Gained programming experience in \texttt{Perl} and \texttt{Ruby} working with software packages like BioPerl and BioRuby}

	\end{itemize}

\item

	\ressubheading{KaKo Industries}{Roswell, GA}{Data Technician}{2005-2007}

	\begin{itemize}

		\resitem{Worked with a small team prewiring CAT5, coaxial, and home security and speaker wires.  Installed systems from small business to major residential outfits}

	\end{itemize}

\end{itemize}


\resheading{Personal}

\begin{itemize}

\item {\bf Hobbies:} Poker, Swimming, Running, Video Games, Building things (physical and/or digital) and watching movie documentaries.

\item {\bf Why Industry over Academia?} I love exploring new problems on the forefront of research, but academia moves too slowly and bureaucratically for me. I enjoy working in a fast-paced environment pushing measurable results to clients on a daily timescale, using the skills that I have honed throughout my academic career.

\item {\bf My Ideal Position:} Working with a fun team solving interesting problems. I enjoy every part of development, from deep backend optimization to client-facing applications and interaction. I would love to make a difference wherever and however I am able while leveraging my machine learning, data mining and mathematical background.

\end{itemize}

\end{document}
